Empowering the use of preprints in ecology and evolution: an exploration of the first 1000 *EcoEvoRxiv* preprints

### 2023-10-14 ms/ms.qmd
Just having a look at the date ranges and number published

pr <- length(unique(data$`Preprint ID`))
```

@@

We downloaded metadata on the `r pr` preprints currently available on *EcoEvoRxiv* (as of the 3rd October 2023).

>>>>

# How many preprints?
  pr <- length(unique(data$`Preprint ID`))

# Dates preprints were published, range and graph
  dates <- range(data$`Published Date`)
```

@@

We downloaded metadata on the `r pr` preprints currently available on *EcoEvoRxiv* (as of the `r gsub("UTC", "", dates[2])`).

```{r, figdates}
#| label: fig-figdates
#| fig-cap: Number of preprints publihsed on *EcoEvoRxiv* across the years.

ggplot(data, aes(x = `Published Date`)) +
  geom_histogram(fill = "grey", color = "black") +
  labs(x = "Published Date", y = "Number of preprints") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```
